---
title: 'Final Project'
author: "Ahiduzzaman"
date: "6/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## The goal of my project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set. I have created a report describing how I have built my model, how I have used cross validation, what I think the expected out of sample error is, and why I made the choices. I have also used my prediction model to predict 20 different test cases.


**Loading libraries

```{r}
library(tidyverse)
library(caret)
library(rpart)
library(rpart.plot)
library(randomForest)
library(rattle)
```


** Reading files

```{r}
set.seed(12)
training=read.csv("C:\\Users\\Acer\\Desktop\\final-project\\pml-training.csv")
testing=read.csv("C:\\Users\\Acer\\Desktop\\final-project\\pml-testing.csv")
```


**Cleaning data

```{r}
feat=names(testing[,colSums(is.na(testing)) == 0])[8:59]
trainclasse = training[,c(feat,"classe")]
testproblem = testing[,c(feat,"problem_id")]
```


**Partioning data

```{r}
inTrain = createDataPartition(trainclasse$classe, p=0.7, list = FALSE)
fortraining = trainclasse[inTrain,]
fortesting = trainclasse[-inTrain,]
```


**Decision tree prediction

```{r}
set.seed(12)
dmodel = rpart(classe ~ ., data = fortraining, method = "class")
fancyRpartPlot(dmodel)
dpredict = predict(dmodel, fortesting, type = "class")
confusionMatrix(factor(dpredict), factor(fortesting$classe))
fortraining$classe=factor(fortraining$classe)
```


**Using random forest for prediction

```{r}
rfmodel=randomForest(classe~.,data=fortraining)
rfpredict=predict(rfmodel,fortesting,type = "class")
fortesting$classe=factor(fortesting$classe)
confusionMatrix(rfpredict,fortesting$classe)
```

--We can see that the random forest prediction has been pretty accurate (99.67%) for the testing data. So will use the random forrest model for this


**Random forest model to predict and submitting

```{r}
finalpredict <- predict(rfmodel, testing, type = "class")
finalpredict
```
